---
title: An Example R Markdown Document
subtitle: (A Subtitle Would Go Here if This Were a Class)
author: Maik Thalmann
institute: Georg-August-University Göttingen
date: "Where, `r format(Sys.time(), '%d %B, %Y')`"
github: https://mkthalmann.github.io/home/
fontsize: 10pt
output:
 beamer_presentation:
    pandoc_args: 
        - "--highlight=breezedark"  # breezedark for darkmode; tango for lightmode
    template: theme.tex
    citation_package: biblatex
    keep_tex: true
    toc: true
    latex_engine: xelatex
    dev: cairo_pdf
    slide_level: 3
bibliography: ../bibliographyuni.bib
make149: true
darkmode: true
mainfont: "Roboto Condensed"
monofont: "Roboto Mono"
sansfont: "Roboto Condensed"
titlefont: "Canela"
mathfont: "Asana Math"
---

```{r import, echo=FALSE, warning=FALSE, message=FALSE}
# read chunk (does not run code)
darkmode <- TRUE
library(knitr)
read_chunk("setup.R")
```

```{r setup, echo=FALSE, warning=FALSE, message=FALSE}
```

# Pop Songs and Political Science

### Sheena Easton and Game Theory

Sheena Easton describes the following scenario for her baby:

1. Takes the morning train
2. Works from nine 'til five
3. Takes another train home again
4. Finds Sheena Easton waiting for him

### R Stuff {.allowframebreaks}

```{r}
d <- diamonds
head(diamonds, 10)
```

Some text to compare font sizes on this slide.

```{r, echo = T}
library(psych)
desc <- as.data.frame(describeBy(d$price, d$color, mat = T, digits = 2))
kable(desc, booktabs = T) %>%
    kable_styling(latex_options = "scale_down")
```

### Plot

```{r}
ggplot(d, aes(x = carat, y = price)) +
    stat_summary(fun = mean, geom = "line", color = mygreen)
```

### Rick Astley's Re-election Platform

Rick Astley's campaign promises:

- Never gonna give you up.
- Never gonna let you down.
- Never gonna run around and desert you.
- Never gonna make you cry.
- Never gonna say goodbye.
- Never gonna tell a lie and hurt you.

Are these promises (if credible) sufficient to secure re-election?

### Rick Astley and Median Voter Theorem

Whereas these pledges conform to the preferences of the **median voter**, we expect Congressman Astley to secure re-election.

### Caribbean Queen and Operation Urgent Fury

Billy Ocean released "Caribbean Queen" in 1984.

- Emphasized sharing the same dream
- Hearts beating as one

"Caribbean Queen" is about the poor execution of Operation Urgent Fury.

- Echoed JCS chairman David Jones' frustrations with military establishment.

Billy Ocean is advocating for what became the Goldwater-Nichols Act.

- Wanted to take advantage of **economies of scale**, resolve **coordination problems** in U.S. military.

### The Good Day Hypothesis

We know the following about Ice Cube's day.

1. The Lakers beat the Supersonics.
2. No helicopter looked for a murder.
3. Consumed \alert{Fatburger} at 2 a.m.
4. Goodyear blimp: "Ice Cube's a pimp." @heimkratzer1998semantics
5. [@posner1980semantics;@hintikka1969semantics;@gries2013statistics;@grice1989studies;@groenendijkstokhof1984questions}]

### The Good Day Hypothesis

\begin{tikzpicture}[baseline=(top.base), scale=.8]
    \Tree [.\node(top){DP}; [.D der ] [.NP [.AP [.A große ] ] [.N$''''$ [.AP^2 [.A^2 verschüchterte ] ] [.N$'''$ [.AP^3 [.A^3 fliegende ] ] [.N$''$ [.N$'$ [.N Wolf ] ] [.PP [.P aus ] [.NP^2 [.N^2 Twilight ] ] ] ] ] ] ] ]
\end{tikzpicture}

### The Good Day Hypothesis

\begin{quotebox}
    Colorless green ideas sleep furiously\hfill (Noam Chomsky)
\end{quotebox}

\begin{rulebox}
    \textbf{\color{mygreen} Functional Application (FA)}\hfill {\footnotesize H\&K:49}\\Wenn $\alpha$ ein verzweigender Knoten ist, \{$\beta$, $\gamma$\} die Menge von $\alpha$'s Töchtern ist und \sem{$\symbf{\beta}$} eine Funktion ist, dessen Domäne \sem{$\symbf{\gamma}$} enthält, dann \sem{$\symbf{\alpha}$} = \sem{$\symbf{\beta}$}(\sem{$\symbf{\gamma}$}).
\end{rulebox}

### Semantics

\begin{exe}
  \ex Lexikoneinträge
  
  \sem{not} = $\lambda p \in D_t$ . $p=0$\\
	\sem{Carla} = Carla\\
	\sem{invite} = $\lambda x \in D_e$ . [$\lambda y \in D_e$ . $y$ lädt $x$ ein]\\
	\sem{a} = $\lambda f \in D_{\langle e, t\rangle}$ . $[\lambda g \in D_{\langle e, t\rangle}$ . es gibt ein $x$, sodass $f(x)=1$ und $g(x)=1]$\\
	\sem{politician} = $\lambda x \in D_e$ . $x$ ist ein Politiker
\end{exe}

### The Good Day Hypothesis

This leads to two different hypotheses:

- $H_0$: Ice Cube's day is statistically indistinguishable from a typical day.
- $H_1$: Ice Cube is having a good (i.e. greater than average) day.

These hypotheses are tested using archival data of Ice Cube's life.

### Stats

```{r stats}
diamonds$id <- 1:length(diamonds$carat)

fit <- aov_ez("id", "price", between = c("color", "cut"), data = diamonds)
```

1. Color: `r apa_print(fit)$full_result$color`
1. Cut: `r apa_print(fit)$full_result$cut`
1. Color:Cut: `r apa_print(fit)$full_result$color_cut`

```{r results='asis'}
apa_table(
    apa_print(fit)$table,
    format = "latex",
    caption = "Test Table"
)
```

# All Code {.unlisted .unnumbered}

## All The Code I Used {.unlisted .unnumbered .allowframebreaks}

```{r get-labels, echo = FALSE}
labs <- knitr::all_labels()
labs <- setdiff(labs, c("import", "setup", "get-labels"))
```

```{r all-code, ref.label=labs, eval = FALSE, echo = TRUE}
```