---
title: An Example R Markdown Document
subtitle: (A Subtitle Would Go Here if This Were a Class)
author: Maik Thalmann
institute: Georg-August-University Göttingen
date: "Where, `r format(Sys.time(), '%d %B, %Y')`"
github: https://mkthalmann.github.io/home/
fontsize: 10pt
output:
 beamer_presentation:
    pandoc_args: "--highlight=breezedark"
    template: theme.tex
    citation_package: biblatex
    keep_tex: true
    latex_engine: xelatex
    dev: cairo_pdf
    slide_level: 3
bibliography: ../bibliographyuni.bib
make149: true
mainfont: "Roboto Condensed"
monofont: "Roboto Mono"
sansfont: "Roboto Condensed"
titlefont: "Roboto Slab Light"
mathfont: "Asana Math"
---

```{r setup, include=FALSE, cache=F, message=F, warning=F, results="hide"}
knitr::opts_chunk$set(cache=TRUE, echo = FALSE, warning = FALSE, message = FALSE)
knitr::opts_chunk$set(fig.path='figs/', fig.align = 'center', fig.asp = 0.6, 
    out.width = '90%', dev.args = list(bg = 'transparent'))
knitr::opts_chunk$set(cache.path='cache/')
knitr::opts_chunk$set(tidy = "styler", tidy.opts = list(scope = "indention"))
library(here)
library(tidyverse)
library(knitr)
library(kableExtra)
library(hrbrthemes)

mygreen <- "#9fd6df"
myred <- "#fc7fb2"

# nicer plots
theme_maik <- function() {
    theme_ipsum_rc() %+replace%
        theme(
            panel.grid.major.x = element_blank(),
            panel.grid.minor.x = element_blank(),
            panel.grid.major.y = element_line(colour = 'gray'),
            panel.grid.minor.y = element_line(colour = 'gray'),
            panel.spacing = unit(.5, "lines"),
            plot.margin = unit(c(.1, .1, .1, .1), "cm"),
            axis.line = element_line(colour = 'gray', size = .5),
            strip.text.x = element_text(size = 9, color = "white"),
        ) + 
        theme(
            axis.title.x = element_text(size = 20, color = "white"),
            axis.title.y = element_text(size = 20, color = "white"),
            axis.text.x = element_text(size = 18, color = "white"),
            axis.text.y = element_text(size = 18, color = "white"),
            axis.ticks = element_line(colour = 'gray')
        )
}
```

# Pop Songs and Political Science

### Sheena Easton and Game Theory

Sheena Easton describes the following scenario for her baby:

1. Takes the morning train
2. Works from nine 'til five
3. Takes another train home again
4. Finds Sheena Easton waiting for him

### R Stuff

```{r}
d <- diamonds
head(diamonds)
```

### R Stuff

Some text to compare font sizes on this slide.

```{r, echo = T}
library(psych)
desc <- as.data.frame(describeBy(d$price, d$color, mat = T, digits = 2))
kable(desc, booktabs = T) %>%
    kable_styling(latex_options = "scale_down")
```

### Plot

```{r}
ggplot(d, aes(x = carat, y = price)) +
    stat_summary(fun.y = mean, geom = "line", color = mygreen) +
    theme_maik()
```

### Rick Astley's Re-election Platform

Rick Astley's campaign promises:

- Never gonna give you up.
- Never gonna let you down.
- Never gonna run around and desert you.
- Never gonna make you cry.
- Never gonna say goodbye.
- Never gonna tell a lie and hurt you.

Are these promises (if credible) sufficient to secure re-election?

### Rick Astley and Median Voter Theorem

Whereas these pledges conform to the preferences of the **median voter**, we expect Congressman Astley to secure re-election.

### Caribbean Queen and Operation Urgent Fury

Billy Ocean released "Caribbean Queen" in 1984.

- Emphasized sharing the same dream
- Hearts beating as one

"Caribbean Queen" is about the poor execution of Operation Urgent Fury.

- Echoed JCS chairman David Jones' frustrations with military establishment.

Billy Ocean is advocating for what became the Goldwater-Nichols Act.

- Wanted to take advantage of **economies of scale**, resolve **coordination problems** in U.S. military.

### The Good Day Hypothesis

We know the following about Ice Cube's day.

1. The Lakers beat the Supersonics.
2. No helicopter looked for a murder.
3. Consumed \alert{Fatburger} at 2 a.m.
4. Goodyear blimp: "Ice Cube's a pimp." @heimkratzer1998semantics
5. [@posner1980semantics;@hintikka1969semantics;@gries2013statistics;@grice1989studies;@groenendijkstokhof1984questions}]

### The Good Day Hypothesis

\begin{tikzpicture}[baseline=(top.base), scale=.8]
    \Tree [.\node(top){DP}; [.D der ] [.NP [.AP [.A große ] ] [.N$''''$ [.AP^2 [.A^2 verschüchterte ] ] [.N$'''$ [.AP^3 [.A^3 fliegende ] ] [.N$''$ [.N$'$ [.N Wolf ] ] [.PP [.P aus ] [.NP^2 [.N^2 Twilight ] ] ] ] ] ] ] ]
\end{tikzpicture}

\begin{quotebox}
    Colorless green ideas sleep furiously
\end{quotebox}

### Semantics

\begin{exe}
  \ex Lexikoneinträge
  
  \sem{not} = $\lambda p \in D_t$ . $p=0$\\
	\sem{Carla} = Carla\\
	\sem{invite} = $\lambda x \in D_e$ . [$\lambda y \in D_e$ . $y$ lädt $x$ ein]\\
	\sem{a} = $\lambda f \in D_{\langle e, t\rangle}$ . $[\lambda g \in D_{\langle e, t\rangle}$ . es gibt ein $x$, sodass $f(x)=1$ und $g(x)=1]$\\
	\sem{politician} = $\lambda x \in D_e$ . $x$ ist ein Politiker
\end{exe}

### The Good Day Hypothesis

This leads to two different hypotheses:

- $H_0$: Ice Cube's day is statistically indistinguishable from a typical day.
- $H_1$: Ice Cube is having a good (i.e. greater than average) day.

These hypotheses are tested using archival data of Ice Cube's life.
